A partisan affair: Mapping patronage in municipal bureaucracies of Brazil

### 2021-03-19 paper/draft.tex
keep editing main text

Regarding partisan duration spells, a few patterns emerge as in the . The spikes every four years mirror the jumps in partisanship in Figure \ref{fig:number_partisan} are mirrored

>>>>

Disaggregating the data further into regions, we find significant heterogeneities with respect to regional trends (Figure \ref{fig:number_partisan_region}).The region that concentrates the most rapid growth and the largest amount of party members is the Southeast, a densely populated and most economically developed region in Brazil. It is closely followed by the Northeast, a region that although relatively poor, has a been characterized by deep partisan roots that underlie patronage exchanges \citep{ansell2010auctioning}. The South, an affluent but predominantly rural region has similar levels of partisanship to the Northeast. In contrast, party membership in the Northern and Midwestern regions are low.

\begin{figure}[H]
    \centering
    \includegraphics[width = 10cm, height = 8cm]{figures/partisanship/plot_partisan_by_year.pdf}
    \caption{\textbf{Number of active party members by year}. There has been a rapid growth in the number of party members in the period between 1997 and 2020.}
    \label{fig:number_partisan_region}
\end{figure}

Regarding partisan duration spells, a few patterns emerge as in the. The spikes every four years mirror the jumps in partisanship in Figure \ref{fig:number_partisan} are mirrored
